COVID-19 Vaccine Acceptance and Hesitancy in Low and Middle Income Countries: Replication Code

### 2021-07-01 2_tables.Rmd
check and comment

---
title: 'COVID-19 Vaccine Acceptance and Hesitancy in Low and Middle Income Countries: Replication Code'
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    number_sections: yes
    theme: cosmo
    code_folding: hide
    toc: yes
  bookdown::html_document2: default
---

@@

@@

@@

  data %>% 
    {
      plyr::adply(.data = combn(unique(.var), loo_n), 
                  .margins = 2, 
                  .fun = function(x) loo_fun(.[!(.var %in% x), ]) )
    }
}

@@

## Final cleaning and harmonization of weights

@@

# If no cluster information given for a study then individuals are clusters 
# Ensure cluster ids are distinct across studies
df <- 
  df %>% 
  dplyr::group_by(study) %>% 
  dplyr::mutate(
    cluster = ifelse(is.na(cluster), paste(1:n()), cluster),
    cluster = paste0(gsub(" ", "_", tolower(country)), "_", cluster))

@@

```{r, fig.height = 13, fig.width = 6}
df %>% 
  select(country, gender, educ) %>%
  gather(category, value, -country) %>%
    ggplot(aes(value)) +  geom_bar() + facet_grid(country ~ category, scales = "free")

@@

@@

loo_estimates <- 
  plyr::ldply(
    .data = list(1,2), 
    .fun = function(x) {
      df %>% 
        dplyr::filter(dplyr::if_all(c(take_vaccine_num, cluster, weight), ~ !is.na(.))) %>% 
        dplyr::filter(!(country %in% c("USA", "Russia"))) %>% 
        loo_helper(., "country", loo_n = x) %>% 
        dplyr::mutate(m = paste0("Leaving ", x, " out"), tag = "All", var = "All")
    })

@@

loo_estimates %<>% 
  dplyr::mutate(
    var = factor(var, levels = c("All", "By gender", "By education", "By age")),
    tag = factor(
      tag, ordered = TRUE,
      levels = rev(c("Female", "Male", "Up to Secondary", 
                       "> Secondary", "<25", "25-54", "55+", "All")),
      labels = rev(c("Female", "Male", "Up to Secondary", 
                     "More than Secondary", "$< 25$", "$25-54$", "$55 +$", "All")))
  ) %>% 
  dplyr::select(var, m, tag, estimate)

@@

# Analysis of differences in means only LMICs
# Notice that Uganda 1 is dropped, because of it does not have reference categories for gender or age
# Notice that we are using df (and not df2) as data, since it does not include "All"

@@

## Reasons to take or not to take

### Table: Reasons to take the vaccine.

@@

```
## Reasons to take by age
```{r, fig.width = 10, fig.height = 7}

@@

## Figure 2: reasons not to take

### Figure

@@

## Figure 3: Trust vaccines

### Figure

@@

## Figure broken down by acceptance

@@

### By gender

@@

>>>>

---
title: 'COVID-19 Vaccine Acceptance and Hesitancy in Low and Middle Income Countries: Replication Code'
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    number_sections: yes
    theme: cosmo
    code_folding: hide
    toc: yes
    toc_float: yes
    self_contained: yes
  bookdown::html_document2: default
keywords: vaccine hesitancy
---

@@

This replication file and ancillary data and code are hosted at https://github.com/wzb-ipi/covid_vaccines_nmed

@@

Aggregated data can be downloaded directly from: https://wzb-ipi.github.io/covid_vaccines_nmed/combined.csv

@@

  # Data is recombined and loo_fun applied to each combination 
  data %>% 
    {
      plyr::adply(.data = combn(unique(.var), loo_n), 
                  .margins = 2, 
                  .fun = function(x) loo_fun(.[!(.var %in% x), ]) )
    }
}

# Illustration of loo_helper
# loo_helper(
#   data = data.frame(country = 1:3, Y = 1:3),
#   loo_n = 2,
#   sample_var = "country",
#   loo_fun = function(dat) mean(dat$Y) 
# )

@@

## Data preparation

Load data:

@@

```{r}
# If no cluster information given for a study then individuals are clusters 
# Ensure cluster ids are distinct across studies
df <- 
  df %>% 
  dplyr::group_by(study) %>% 
  dplyr::mutate(
    cluster = ifelse(is.na(cluster), paste(1:n()), cluster),
    cluster = paste0(gsub(" ", "_", tolower(country)), "_", cluster))

@@

```{r, fig.height = 13, fig.width = 15}
df %>% 
  select(country, gender, educ) %>%
  gather(category, value, -country) %>%
    ggplot(aes(value)) +  geom_bar() + facet_grid(country ~ category, scales = "free")

@@

The following code produces all figures and tables from the paper as well as cited statistics and supplementary material.

@@

# Loo estimates for all LMIC respondents
loo_estimates <- 
  plyr::ldply(
    .data = list(1,2), 
    .fun = function(x) {
      df %>% 
        dplyr::filter(dplyr::if_all(c(take_vaccine_num, cluster, weight), ~ !is.na(.))) %>% 
        dplyr::filter(!(country %in% c("USA", "Russia"))) %>% 
        loo_helper(., "country", loo_n = x) %>% 
        dplyr::mutate(m = paste0("Leaving ", x, " out"), tag = "All", var = "All")
    })

# Loo estimates broken down by category (appended to above)

@@

# Clean up labels
loo_estimates %<>% 
  dplyr::mutate(
    var = factor(var, levels = c("All", "By gender", "By education", "By age")),
    tag = factor(
      tag, ordered = TRUE,
      levels = rev(c("Female", "Male", "Up to Secondary", 
                       "> Secondary", "<25", "25-54", "55+", "All")),
      labels = rev(c("Female", "Male", "Up to Secondary", 
                     "More than Secondary", "$< 25$", "$25-54$", "$55 +$", "All")))
  ) %>% 
  dplyr::select(var, m, tag, estimate)

@@

# Analysis of differences in means only LMICs
# Notice that Uganda 1 is dropped, because it does not have reference categories for gender or age
# Notice that we are using df (and not df2) as data, since it does not include "All"

@@

## Reasons

### Table: Reasons to take

@@

### Reasons to take (by age)

@@

### Figure 2: reasons not to take

@@

## Trust

### Main figure (Fig 3)

@@

### ...by acceptance

@@

### ...by gender

@@

### Trusted Sources Table
